\section{Trends \& Motivation}

Common problems seen in datacenters. Probably need a graph for each one of these
\begin{myitemize}
  \item  Some tasks are very short/small and others are very large (in terms of
    resource usage) and long (in terms of time) \todo{Graph}.  
    Scheduling these is difficult; 

  \item Stragglers are exacerbated by the above problem~\todo{Graph}: if a task
    ends up on a machine with a large task consuming tons-o-resources, it will
    straggle

  \item Hot spots: there are hot spots in network usage, and also on machines
    that host popular data
\end{myitemize}

Make a table of problems caused by power-law distributions and papers about
them (should make this more concrete/compelling)

Datacenters and workloads are changing
\begin{myitemize}
  \item Focus is on main memory workloads, with need for low latency. Use the
    MapReduce$\rightarrow$Dremel$\rightarrow$Spark Streaming data here.
  \item Networks have grown to be fast making disk locality irrelevant. This
    means getting data from a remote location is fast. Further networks don't
    have a fixed overhead of transfer. Disk-based stuff uses 64MB to amortize
    that cost. \todo{Numbers ?}
  \item SSDs are becoming cheaper - Fast random access with low access time.
    With growing memory sizes + SSD, it is feasible to fetch most of the data
    without hitting the disk (local or remote).
  \item Need for low latency and ability to exploit fast-data access leads to
    tiny tasks
\end{myitemize}
